Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-03-10 manuscript/appendix.Rmd
rearranged/ re-numbered SI figures
closes #65

  knitr::include_graphics("tables_figures/climate_regressions.png")
```
\elandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among FACF as a function of latitude and climate variables", out.width ='100%', fig.pos='H'}

>>>>

  knitr::include_graphics("tables_figures/climate_regressions.png")
```
\elandscape

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among FACF as a function of latitude and climate variables", out.width ='80%', fig.pos='H'}
